\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-19 metatheory.tex
comment

% Motivation of using QIIT
We start with the formulation of the syntax in the declarative style, which is based on the
formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT)~\cite{martin1982constructive}
given by~\citet{coquand2018canonicity}. 
% Thus we will omit a great deal of details about MLTT here
\YZ{What details are omitted?} 
We will mainly focus on the new facility that we introduced

>>>>

% Motivation of using QIIT
We start with the formulation of the syntax in the declarative style, which is based on the
formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT)~\cite{martin1982constructive}
given by~\citet{coquand2018canonicity}.\YZ{
    What's the relation to the CIC underlying Coq, given that the implementation is a Coq plugin?
}
% Thus we will omit a great deal of details about MLTT here
We will mainly focus on the new facility that we introduced.
